Working Principles of Proof Assitants and Formalization of Some Proofs in Agda

### 2025-06-03 Presentation/Presentation.tex
Finishing up the project proposal presentation small edits in proofs

\usepackage[utf8]{inputenc}
\usepackage{graphicx}  
\usepackage{amsmath}   
\usepackage{hyperref}  
\usepackage{url}       
\usepackage{cite}

@@

\section{Methodology and Tool}
\begin{frame}{Methodology}

\end{frame}
\begin{frame}{Agda}
Agda is a functional programming language with dependent types. It is based on Martin Löf Type Theory. And most importantly it is a proof assitant.
\cite{inproceedings}
\end{frame}
\begin{frame}{Why Agda?}
\end{frame}

\section{Work Plan}
\begin{frame}{Work Plan}
\end{frame}

\section{Significance and Expected Outcomes}
\begin{frame}{Significance}
\end{frame}
\begin{frame}{Expected Outcomes}
\end{frame}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}  
\usepackage{amsmath}   
\usepackage{hyperref}  
\usepackage{url}       
\usepackage{cite}
\usepackage{booktabs}

@@

\section{Methodology and Tool}
\begin{frame}{Methodology}
    \begin{itemize}
      \item Investigating the Coq and the agda proof assistant
      \item Assessing the logic behind each of these proof assistants
      \item Investigating How to formalized proofs in Agda
    \end{itemize}
\end{frame}
\begin{frame}{Agda}
Agda is a functional programming language with dependent types. It is based on Martin Löf Type Theory. And most importantly it is a proof assitant.
\cite{inproceedings}
\end{frame}
\begin{frame}{Why Agda?}
  \begin{itemize}
    \item Dependently Typed programming language
    \item Fully embraces the Curry–Howard isomorphism
    \item Minimal where users typically define the core logical construct from small set of primitives
    \item Active Community
  \end{itemize}
\end{frame}

\section{Work Plan}
\begin{frame}{Work Plan}
      \begin{tabular}{p{1cm} p{8cm} }
        \toprule
        Week & Work plan \\
        \toprule
         1 & Understanding (Dependent) Type Theory and Proof Theory\\
        \midrule
         2 & Understanding the implementation of type theory models in digital proof assistant \\
        \midrule
         3 & Understanding Purely functional Programming paradigm and $ \lambda $-calculus\\
        \midrule
         4 & Working Principles of Agda and its core implementation \\
        \midrule 
         5 & Formalization of some proofs in Agda \\
        \bottomrule

    \end{tabular}
\end{frame}

\section{Significance and Expected Outcomes}
\begin{frame}{Significance}
  \begin{itemize}
    \item Writing proofs in a formal language adds rigor and reduces ambiguity, allowing proof assistants to treat proofs as executable code that can be mechanically checked, shifting trust from human readers to computers and minimizing errors in mathematical verification.

   \item Using the same theoretical foundation, treating programs as proofs and verifying their correctness increases reliability, ensuring that code—especially for sensitive applications—is secure and functions exactly as intended.

  \end{itemize}
\end{frame}
\begin{frame}{Expected Outcomes}
  \begin{itemize}
    \item Understanding of dependent type theory and logics
    \item Understanding of $\lambda$-calculus and purely functional programming
    \item  Formalization of some selected proofs in agda
  \end{itemize}
\end{frame}
